---
title: "Cabbages"
author: "Gracie Telles"
date: "Fall 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
library(ggplot2)
library(dplyr)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 
The cabbages data from the MASS package is loaded into a dataframe called veggy. We need to find out if there is a difference in average VitC between c39 and c52 cultivation methods.
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

$H_0$ There is no difference in the vitamin C content of cabbages based on cultivation method.

$H_A$ There is a difference in the vitamin C content of cabbages based on the cultivation method.

# Methods

```{r}
data = veggy
```

Vitamin C content is a numerical variable, and cultivation method is a categorical variable. Therefore, we use the Numerical-Cat helper file.

# Results
## Descriptive Results

# Results
### Graphical Descriptive Results

```{r}
ggplot(data, aes(x = Cult, y = VitC)) +
  geom_boxplot() +
  labs(x = "Cult", y = "VitC") +
  theme_minimal()

```

The box plot shows that there is a difference in vitamin C content in method C52 and C39. The median of vitamin C in C52 is higher than the median of vitamin C in C39 by around 15 IUs.


### Numerical Descriptive Results

```{r}
num_summary <- data %>%
  group_by(Cult) %>%
  summarise(
    Mean = mean(VitC),
    Median = median(VitC),
    SD = sd(VitC)
  )

num_summary

```

Cultivation method 39 has a mean of 51.5 vitamin C content, while cultivation method 52 has an mean of 64.4 vitamin C content.


## Inferential Results

```{r}
 t.test(VitC ~ Cult, data = data)

```

The p value is equal to 0.00000003405. This p value is lower than 0.05, so we reject the null hypothesis- there is a difference in the average number of vitamin C between method C39 and C52.


# Discussion and Conclusion

There is a difference between the vitamins in our numerical and graphical results. The cultivation method 52 provided more vitamin C in the cabbages on average compared to cultivation method 39. The data shows the average vitamin C in C39 was 51.5, and C52 was 64.4. The p value is lower than 0.05, so we reject the null hypothesis. The cultivation method 52 provided more vitamin C in the cabbages on average compared to cultivation method 39. 